---
title: "Workflow"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: true
---

**start fresh** - check your global options

This is a script to .....


### Naming conventions:
  - ALL_CAPS: hard-coded constants 
  - lowerCamelCase: variables, functions
  - myXYZ: designates global utility functions from my general library



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)


# Side note----

pkgs = c("tidyverse", "plotly" )

loadPackages = function(pkgs){

  temp.packages = function(a){
      if(!require(a, character.only = TRUE)){
        install.packages(a)
        library(a, character.only = TRUE)
      }
    }

  lapply(pkgs, load.packages)

}


sapply(list.files(pattern="[.]R$", path="./Functions", full.names=TRUE), source)


```


### Load your data

 - relative pathways
 - tab complete
 - watch out for things like white spaces and factors
 - check data class
 
 **bold** *italics* 
```{r load_data}
irisRaw <- read.csv("data_raw/iris_dataset.csv")

```
  
```{r}
summary(irisRaw)

head(irisRaw)
```
 
 
### Clean your data

```{r filter_setosa}
irisClean <- irisRaw %>%
  filter(Species == "setosa")
```
 
 
 ### Simple graph
```{r}

```

###Exporting your graph
```{r}

```
 
 