---
title: "Workflow"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: true
---

**start fresh** - check your global options

**Purpose:**

This is a script to .....

*Created*: November 15,2018

*Updated*: November 16, 2018


### Naming conventions:
  - ALL_CAPS: hard-coded constants 
  - lowerCamelCase: variables, functions
  - myXYZ: designates global utility functions from my general library



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)




```


### Load your data

 - relative pathways
 - tab complete
 - watch out for things like white spaces and factors
 - check data class
 
This is **bold** and this is *italics* . 

```{r load_data}

irisRaw <- read.csv("data_raw/iris_dataset.csv")

```
  
```{r review_data}
summary(irisRaw)

head(irisRaw)
```
 
 
### Clean your data

```{r filter_setosa}

irisClean <- irisRaw %>%
  filter(Species == "setosa")
```
 
 
 ### Simple graph
 
 Petal length vs petal width
 
```{r plot}

ggplot(irisClean, aes())
```

###Exporting your graph

```{r save}

ggsave()
```
 
 